---
title: "Results"
format: 
  html:
    toc: true
    toc-location: left
    code-fold: true
---

## Set up and code
```{r setup}
library(DT)
library(here)
library(tidyverse)
full_data <- readRDS(here("data", "vaccine_impact.RDS"))

cume_cases <- full_data |>
    group_by(population, scenario) |> 
    mutate(cume_estimate = cumsum(estimate),
           cume_estimate_lower = cumsum(lower), 
           cume_estimate_upper = cumsum(upper)) |>
    ungroup()


## No vaccination
INFANT_HOSP_NOVAC <- cume_cases |> 
    filter(population == "infant", 
           scenario == "observed",
           date == max(date)) |> 
    pull(cume_estimate) |> 
    round() |> 
    prettyNum(big.mark = ",")

PREGNANT_HOSP_NOVAC <- cume_cases |> 
    filter(population == "pregnant", 
           scenario == "observed",
           date == max(date)) |> 
    pull(cume_estimate) |> 
    round() |> 
    prettyNum(big.mark = ",")

## 100% vaccination
AVERTED_INFANT_V100 <- cume_cases |>
    filter(population == "infant",
        scenario == "vaccine100",
        date == max(date)) |>
    transmute(label = sprintf("%s (95%% CI: %s - %s)",
        prettyNum(round(cume_averted), big.mark = ","),
        prettyNum(round(cume_averted_lower), big.mark = ","),
        prettyNum(round(cume_averted_upper), big.mark = ","))
    ) |> 
    pull(label)

AVERTED_PREGNANT_V100 <- cume_cases |>
    filter(population == "pregnant",
        scenario == "vaccine100",
        date == max(date)) |>
    transmute(label = sprintf("%s (95%% CI: %s - %s)",
        prettyNum(round(cume_averted), big.mark = ","),
        prettyNum(round(cume_averted_lower), big.mark = ","),
        prettyNum(round(cume_averted_upper), big.mark = ","))
    ) |> 
    pull(label)

## 50% vaccination
AVERTED_INFANT_V50 <- cume_cases |>
    filter(population == "infant",
        scenario == "vaccine50",
        date == max(date)) |>
    transmute(label = sprintf("%s (95%% CI: %s - %s)",
        prettyNum(round(cume_averted), big.mark = ","),
        prettyNum(round(cume_averted_lower), big.mark = ","),
        prettyNum(round(cume_averted_upper), big.mark = ","))
    ) |> 
    pull(label)

AVERTED_PREGNANT_V50 <- cume_cases |>
    filter(population == "pregnant",
        scenario == "vaccine50",
        date == max(date)) |>
    transmute(label = sprintf("%s (95%% CI: %s - %s)",
        prettyNum(round(cume_averted), big.mark = ","),
        prettyNum(round(cume_averted_lower), big.mark = ","),
        prettyNum(round(cume_averted_upper), big.mark = ","))
    ) |> 
    pull(label)

## 15% vaccination
AVERTED_INFANT_V15 <- cume_cases |>
    filter(population == "infant",
        scenario == "vaccine15",
        date == max(date)) |>
    transmute(label = sprintf("%s (95%% CI: %s - %s)",
        prettyNum(round(cume_averted), big.mark = ","),
        prettyNum(round(cume_averted_lower), big.mark = ","),
        prettyNum(round(cume_averted_upper), big.mark = ","))
    ) |> 
    pull(label)

AVERTED_PREGNANT_V15 <- cume_cases |>
    filter(population == "pregnant",
        scenario == "vaccine15",
        date == max(date)) |>
    transmute(label = sprintf("%s (95%% CI: %s - %s)",
        prettyNum(round(cume_averted), big.mark = ","),
        prettyNum(round(cume_averted_lower), big.mark = ","),
        prettyNum(round(cume_averted_upper), big.mark = ","))
    ) |> 
    pull(label)
```


## Text

Under a scenario without COVID-19 vaccination during pregnancy, we estimated a total of `r INFANT_HOSP_NOVAC` COVID-19 hospitalizations of young infants (in a population of 1.83 million) and `r PREGNANT_HOSP_NOVAC` COVID-19 hospitalizations of pregnant persons (in a population of 3 million) over the study period of January 2024 – May 2025. Under 50% or 100% coverage of COVID-19 vaccination during pregnancy, we estimated `r AVERTED_INFANT_V50` and `r AVERTED_INFANT_V100` averted COVID-19 hospitalizations in young infants and `r AVERTED_PREGNANT_V50` and `r AVERTED_PREGNANT_V100` averted severe COVID-19 cases in pregnant persons, respectively. However, in scenarios of low vaccine coverage (recent vaccination uptake during pregnancy: 15%), we estimated vaccination averted `r AVERTED_INFANT_V15` COVID-19 hospitalizations in young infants and `r AVERTED_PREGNANT_V15` severe cases in pregnant persons. These results are sensitive to COVID-19 incidence, clinical severity, and vaccine effectiveness estimates.

## Interactive table

```{r interactivetable}
cume_cases |>
    filter(scenario != "observed") |>
    select(population, scenario, date, estimate, starts_with("averted")) |>
    rowwise() |>
    transmute(
        population_cat = factor(population,
            levels = c("infant", "pregnant"),
            labels = c("Infant (0-6 months)", "Pregnant"),
            ordered = TRUE),
        scenario_cat = factor(scenario,
            levels = c("vaccine15", "vaccine50", "vaccine100"),
            labels = c("15% vaccination", "50% vaccination", "100% vaccination"),
            ordered = TRUE),
        date,
        estimated_cases = estimate,
        averted_cases = sprintf("%s (95%% CI: %s - %s)",
            prettyNum(round(averted), big.mark = ","),
            prettyNum(round(averted_lower), big.mark = ","),
            prettyNum(round(averted_upper), big.mark = ","))
    ) |>
    arrange(population_cat, desc(scenario_cat), date) |>
    DT::datatable(
        colnames = c(
            "Population",
            "Vaccine scenario",
            "Date",
            "Estimated cases",
            "Averted cases"
        ),
        rownames = FALSE,
        filter = list(
            position = "top"
        )
    )
```
